### 2024-06-18 basic-statistics.qmd
20240618 - fix table

| Number                                   | Misconception
|:----------------------------------------------------|:------------|
| 1 If $p = .05$, the null hypothesis has only a 5% chance of being true.
| 2 A nonsignificant difference (eg, $p > .05$) means there is no difference between groups.
| 3 A statistically significant finding is clinically important.
| 4 Studies with $p$-values on opposite sides of .05 are conflicting.
| 5 Studies with the same $p$-value provide the same evidence against the null hypothesis.
| 6 $p = .05$ means that we have observed data that would occur only 5% of the time under the null hypothesis.
| 7 $p = .05$ and $p < .05$ mean the same thing.
| 8 $p$-values are properly written as inequalities (e.g., "$p \le .05$" when $p = .015$)
| 9 $p = .05$ means that if you reject the null hypothesis, the probability of a Type I error is only 5%.
| 10 With a $p = .05$ threshold for significance, the chance of a Type I error will be 5%.
| 11 You should use a one-sided $p$-value when you don't care about a result in one direction, or a difference in that direction is impossible.
| 12 A scientific conclusion or treatment policy should be based on whether or not the $p$-value is significant.

>>>>

| Number | Misconception                                                                                                                              |
|:-------|:-------------------------------------------------------------------------------------------------------------------------------------------|
| 1      | If $p = .05$, the null hypothesis has only a 5% chance of being true.                                                                      |
| 2      | A nonsignificant difference (eg, $p > .05$) means there is no difference between groups.                                                   |
| 3      | A statistically significant finding is clinically important.                                                                               |
| 4      | Studies with $p$-values on opposite sides of .05 are conflicting.                                                                          |
| 5      | Studies with the same $p$-value provide the same evidence against the null hypothesis.                                                     |
| 6      | $p = .05$ means that we have observed data that would occur only 5% of the time under the null hypothesis.                                 |
| 7      | $p = .05$ and $p < .05$ mean the same thing.                                                                                               |
| 8      | $p$-values are properly written as inequalities (e.g., "$p \le .05$" when $p = .015$).                                                     |
| 9      | $p = .05$ means that if you reject the null hypothesis, the probability of a Type I error is only 5%.                                      |
| 10     | With a $p = .05$ threshold for significance, the chance of a Type I error will be 5%.                                                      |
| 11     | You should use a one-sided $p$-value when you don't care about a result in one direction, or a difference in that direction is impossible. |
| 12     | A scientific conclusion or treatment policy should be based on whether or not the $p$-value is significant.                                |
